Synthesis of Linear Functional Programs

### 2021-05-09 article/article.tex

The Curry-Howard correspondence generalizes beyond the simply-typed
$\lambda$-calculus and propositional intuitionistic logic. It extends
to the realms of polymorphism (higher-order logic \todo{review -
  \url{https://en.wikipedia.org/wiki/Lambda_cube}} second-order
propositional calculus), dependent types (first-order predicate
logic), and various other extensions of natural deduction and
simply-typed $\lambda$-calculus -- which include linear logic and
linear types.

>>>>

The Curry-Howard correspondence generalizes beyond the simply-typed
$\lambda$-calculus and propositional intuitionistic logic. It extends
to the realms of polymorphism (higher-order logic $\todo{review -
  \url{https://en.wikipedia.org/wiki/Lambda_cube}}$ second-order
propositional calculus), dependent types (first-order predicate
logic), and various other extensions of natural deduction and
simply-typed $\lambda$-calculus -- which include linear logic and
linear types.
